An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-12-30 EconGrowth.Rnw
energyType:  NA -> "none"

<<CD_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (without energy) resample model parameters.">>=
cdResampleTrianglePlot(energyType=NA, facet_formula = ~ countryAbbrev)
@

@@

<<CES_lambda_gamma_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\lambda$ and $\\gamma$.">>=
cesResamplePlotLambdaGamma(energyType=NA)
@

<<CES_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType=NA)
@

@@

<<CES_sigma_delta_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\rho$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType=NA)
@

@@

<<CES_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (without energy) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
createCESParamsGraph(energyType=NA)
@

@@

<<CD_Params_Table, results='asis'>>=
printCDParamsTable(energyType=NA)    #Without energy
printCDParamsTable(energyType="Q"); printCDParamsTable(energyType="X"); printCDParamsTable(energyType="U") #With energy
@

@@

<<CES_Params_Table, results='asis'>>=
printCESParamsTableA(energyType=NA);  printCESParamsTableB(energyType=NA)
printCESParamsTableA(energyType="Q"); printCESParamsTableB(energyType="Q")
printCESParamsTableA(energyType="X"); printCESParamsTableB(energyType="X")
printCESParamsTableA(energyType="U"); printCESParamsTableB(energyType="U")
@

>>>>

<<CD_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (without energy) resample model parameters.">>=
cdResampleTrianglePlot(energyType="none", facet_formula = ~countryAbbrev)
@

@@

<<CES_lambda_gamma_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\lambda$ and $\\gamma$.">>=
cesResamplePlotLambdaGamma(energyType="none")
@

<<CES_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="none")
@

@@

<<CES_sigma_delta_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\rho$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="none")
@

@@

<<CES_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (without energy) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
createCESParamsGraph(energyType="none")
@

@@

<<CD_Params_Table, results='asis'>>=
printCDParamsTable(energyType="none")    #Without energy
printCDParamsTable(energyType="Q"); printCDParamsTable(energyType="X"); printCDParamsTable(energyType="U") #With energy
@

@@

<<CES_Params_Table, results='asis'>>=
printCESParamsTableA(energyType="none");  printCESParamsTableB(energyType="none")
printCESParamsTableA(energyType="Q"); printCESParamsTableB(energyType="Q")
printCESParamsTableA(energyType="X"); printCESParamsTableB(energyType="X")
printCESParamsTableA(energyType="U"); printCESParamsTableB(energyType="U")
@
